---
title: "Simple document"
output:  github_document

---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r round(mean(samp),2)`.

# Section 3

## Plot from last time

This is going to make a plot! First I generate a dataframe, then use `ggplot` to make a scatterplot.

```{r chunk_scatterplot}
plot_df = 
  tibble(
    x = rnorm(n = 1000),
    y = 1 + 2 * x + rnorm(n = 1000)
  )

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

# Section 4

The chunk below creates a dataframe containing a sample of size 500 from a 
random normal variable, constructs the specified logical vector, takes the 
absolute value of each element of that sample,and produces a histogram of 
the absolute value. The code chunk also finds the median of the sample and
stores it for easy in-line printing.

```{r learning_assessment_1}
library(tidyverse)

la_df = tibble(
  norm_samp = rnorm(500, mean = 1),
  norm_samp_pos = norm_samp > 0,
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x = abs_norm_samp)) + geom_histogram()

median_samp = median(pull(la_df, norm_samp))
```

The median of the variable containing absolute values is 
`r round(median_samp, digits = 2)`.






